Untitled

### 2024-02-05 MSR.rmd
Update

#chi-square(11)  
i <- 1000
lambda <- 2 
alpha < 5
U <- log(runif(i*alpha))  
Um <- matrix(U, i)
Y <- apply(Um, 1, sum) 
chi < --Y/lambda
chi <- chi +(rnorm(i))^2  
hist(chi)
```

>>>>

#chi-square(11)  
i <- 1000
lambda <- 2 
alpha <- 5
U <- log(runif(i*alpha))  
Um <- matrix(U, i)
Y <- apply(Um, 1, sum) 
chi <- -Y/lambda
chi <- chi +(rnorm(i))^2  
hist(chi)
```
